Moral Foundations of U.S. Political News Organizations

### 2019-02-09 pilot_manuscript.Rmd
idk i reinstalled papaja??? also, small update to citations

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

@@

Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@CITE_rvest]. Using this dataset, we identified word count and average word count per source. This process was run once daily starting in February 2018 until March 2018. Starting in mid-March 2018, the process was run twice daily - once in the morning and again in the evening. Data collection was terminated once 250,000 words per source was collected in April 2018.

>>>>

author_note: |

@@

Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016]. Using this dataset, we identified word count and average word count per source. This process was run once daily starting in February 2018 until March 2018. Starting in mid-March 2018, the process was run twice daily - once in the morning and again in the evening. Data collection was terminated once 250,000 words per source was collected in April 2018.
